Talks

### 2025-06-28 talks.qmd
update

- Can AI be used for better matching of proposals to reviewers? Feasibility and formal evaluation with the Metascience 2025 conference. Metascience 2025, June 30 - 2 July, London.

>>>>

- [Can AI be used for better matching of proposals to reviewers? Feasibility and formal evaluation with the Metascience 2025 conference](https://docs.google.com/presentation/d/12LqFL4JlioIgYgUxUCOiDUvTwERgT5Y3/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true). Metascience 2025, June 30 - 2 July, London.
